Operation Mode Study in Cloud Manufacturing Ecosystem

### 2016-09-21 design.tex
modify the strcuture begin

% \subsubsection{Provider respond to type-matched job} % (fold)
% \label{ssub:response_in_type_matched_resource}
Apart from $mr_k$ respond to $t_{ij}$ as we explained above, there are 2 other cases in incubation mode:
\begin{asparaenum}
\item $mr_k$ respond to $sc_l$
\suspend{asparaenum}
If $mr_k$ was type-matched with $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$, provider of $mr_k$ will respond to the service-call. If $mr_k$ was finally selected, both available capacity and capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and these capacity will not be restored even after the finish of $sc_l$ part. Provider of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{l,\tau}$.
\resume{asparaenum}
\item $ms_l$ respond to $t_{ij}$
\end{asparaenum}
Service is task-oriented machine, so if type-matched ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of it will respond to $t_{ij}$ as soon as possible, demander will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.

@@

\begin{asparaenum}
\item Select $mr_k$ for $sc_l$ when $\mathcal{B}_{l,\tau} = \mathcal{A}_l$
\suspend{asparaenum}
Provider of $sc_l$ select resource from $\mathcal{R}_{l,\tau}$ is similar to \autoref{eq:selectresaim}--\ref{eq:decisionvark}, but the difference is that the $\bm{l}_{\alpha}$ here is also a set of selected resources with type $\alpha$, $\bm{l}_{\alpha}$ is subset of decision variable $\bm{l}$. Selected resources capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and if the sum of capacity quantity in $\bm{l}_{\alpha}$ less than the $sc_l$ required, this selection will not to be executed.
\begin{subnumcases}{}
C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\label{eq:capq}\\
C_{k,\tau} := 0 & otherwise \label{eq:cap0}
\end{subnumcases}

\resume{asparaenum}
\item Select $ms_l$ for $t_{ij}$ when $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij},|\mathcal{S}_{ij,\tau}|>0$
\suspend{asparaenum}
This situation implies that the resource candidates are not enough and there exists service candidates.
\begin{equation}
\max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)\label{eq:selectserviceaim}
\end{equation}
\begin{numcases}{\text{s.t.}}
\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \label{eq:servicecomplydist}\\
\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \label{eq:servicecomplydistend}\\
l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \label{eq:decisionvariablel}
\end{numcases}

@@

\resume{asparaenum}
\item Select machine for $t_{ij}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$.
\end{asparaenum}
In this situation, demander of $t_{ij}$ will select ether a bunch of resources with cooperation or one single service, so the key idea here is to pre-select optimal resources and optimal service, then to compare these two optimal options to select the better one.
\begin{equation}
\max_{m\in\{l^*,\bm{k}^*\}} \left( \Delta_m,
Rank_m, \mathcal{L}_m \right) \\ \label{eq:combaim}
% \text{s.t.}\notag
\end{equation}
\begin{numcases}{\text{s.t.}}
% q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
% R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
% \mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
% \bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right]& \\
% k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &\footnotesize$\alpha\in\mathcal{A}_{ij}$ \\
\bm{k}^* = \arg\left(\max_{\forall \bm{k}}\left( \delta_{\bm{k}},
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right)\right) & \label{eq:optk}\\
Rank_{\bm{k}^*} = \min_{k\in\bm{k}^*} \left\{ R\left( F\left( mr_k \right) \right) \right\} & \label{eq:temprank}\\
\mathcal{L}_{\bm{k}^*} = \max_{k\in\bm{k}^*}\left\{ \abs{\mathcal{L}_{k,\tau}} \right\} & \label{eq:templength}\\
\Delta_{\bm{k}^*} \sim \mathcal{N} \left(\mu_{\bm{k}^*},\sigma_{\bm{k}^*}^2\right) & \label{eq:tempqualitystart}\\
\mu_{\bm{k}^*} = mean\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\sigma_{\bm{k}^*} = std\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\bm{mr}_{\bm{k}^*} = \bigcup_{k\in\bm{k}^*}mr_k  &\\
\bm{q}_{\bm{k}^*}  =\bigcup_{\alpha\in\mathcal{A}_{ij}}q_{\alpha,ij} & \label{eq:tempqualityend}\\
% \Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
% \mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
% \sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
% l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \\
l^* = \arg\left( \max_{\forall l}\left(\Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)  \right) & \label{eq:optl}\\
Rank_{l^*} = R\left( F\left( ms_{l^*} \right) \right) & \\
\mathcal{L}_{l^*} = \abs{\mathcal{L}_{l^*,\tau}} & \\
m \in \left\{ l^*,\bm{k}^* \right\} \label{eq:newdicisionvariable}
\end{numcases}

@@

% \subsubsection{Provider assign task to selected machine} % (fold)
Apart from $mr_k$ assign $t_{ij}$, there are 2 other cases in incubation mode:

\begin{asparaenum}
\item Assign $sc_l$ to $mr_k$
\suspend{asparaenum}
If $mr_k$ is selected by provider of $sc_l$ at time $\tau$, the assign condition is more restrict, it should be changed into $\abs{\mathcal{L}_{k,\tau}} = \abs{\mathcal{G}_{k,\tau}} = \abs{\mathcal{H}_{k,\tau}} = 0$, for the capacity dominance feature of service-call, we need to assign this type of job one by one. Then, the provider of $mr_k$ should change the predecessor set:
\begin{equation}
	\mathcal{P}_l := \mathcal{P}_l\cup \mathcal{L}_{k,\tau} \cup \mathcal{H}_{k,\tau}
\end{equation}
and all the task assign after $\tau$, we say $\tau'>\tau$ will set:
\begin{equation}
	\mathcal{P}_{ij} := \mathcal{P}_{ij}\cup \left\{ sc| sc\in\mathcal{L}_{k,\tau'},sc \text{ is service-call} \right\} \cup \mathcal{H}_{k,\tau'}
\end{equation}
And $A_{k,\tau}$ will be changed with the same amount in \autoref{eq:capq}--\ref{eq:cap0}.
\resume{asparaenum}
\item Assign $t_{ij}$ to $ms_l$
\end{asparaenum}
Assign $t_{ij}$ to $ms_l$ is very simple and there will be no semi-active status for $t_{ij}$, hence it will add to $\mathcal{G}_{k,\tau}$ if $\abs{\mathcal{G}_{k,\tau}}=0$, or to $\mathcal{L}_{k,\tau}$ otherwise.
% \begin{subnumcases}{}
% \mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{sc_{l}\} & if $\abs{\mathcal{G}_{k,\tau}}=0$ \\
% \mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{sc_{l}\} & otherwise
% \end{subnumcases}

>>>>

% \subsubsection{Provider respond to type-matched job} % (fold)
% \label{ssub:response_in_type_matched_resource}
\begin{asparaenum}
\item Respond behavior
\suspend{asparaenum}
Apart from $mr_k$ respond to $t_{ij}$ as we explained above, there are 2 other cases in incubation mode:
If $mr_k$ was type-matched with $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$, provider of $mr_k$ will respond to the service-call. If $mr_k$ was finally selected, both available capacity and capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and these capacity will not be restored even after the finish of $sc_l$ part. Provider of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{l,\tau}$.

Service is task-oriented machine, so if type-matched ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of it will respond to $t_{ij}$ as soon as possible, demander will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.

@@

\resume{asparaenum}
\item Select behavior
\suspend{asparaenum}
Select $mr_k$ for $sc_l$ when $\mathcal{B}_{l,\tau}\subset\mathcal{A}_l$

Provider of $sc_l$ select resource from $\mathcal{R}_{l,\tau}$ is similar to \autoref{eq:selectresaim}--\ref{eq:decisionvark}, but the difference is that the $\bm{l}_{\alpha}$ here is also a set of selected resources with type $\alpha$, $\bm{l}_{\alpha}$ is subset of decision variable $\bm{l}$. Selected resources capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and if the sum of capacity quantity in $\bm{l}_{\alpha}$ less than the $sc_l$ required, this selection will not to be executed.

\begin{subnumcases}{}
C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\label{eq:capq}\\
C_{k,\tau} := 0 & otherwise \label{eq:cap0}
\end{subnumcases}

Select $ms_l$ for $t_{ij}$ when $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij},|\mathcal{S}_{ij,\tau}|>0$

This situation implies that the resource candidates are not enough and there exists service candidates.
\begin{equation}
\max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)\label{eq:selectserviceaim}
\end{equation}
\begin{numcases}{\text{s.t.}}
\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \label{eq:servicecomplydist}\\
\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \label{eq:servicecomplydistend}\\
l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \label{eq:decisionvariablel}
\end{numcases}

@@

Select machine for $t_{ij}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$.

In this situation, demander of $t_{ij}$ will select ether a bunch of resources with cooperation or one single service, so the key idea here is to pre-select optimal resources and optimal service, then to compare these two optimal options to select the better one.
\begin{equation}
\max_{m\in\{l^*,\bm{k}^*\}} \left( \Delta_m,
Rank_m, \mathcal{L}_m \right) \\ \label{eq:combaim}
% \text{s.t.}\notag
\end{equation}
\begin{numcases}{\text{s.t.}}
% q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
% R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
% \mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
% \bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right]& \\
% k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &\footnotesize$\alpha\in\mathcal{A}_{ij}$ \\
\bm{k}^* = \arg\left(\max_{\forall \bm{k}}\left( \delta_{\bm{k}},
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right)\right) & \label{eq:optk}\\
Rank_{\bm{k}^*} = \min_{k\in\bm{k}^*} \left\{ R\left( F\left( mr_k \right) \right) \right\} & \label{eq:temprank}\\
\mathcal{L}_{\bm{k}^*} = \max_{k\in\bm{k}^*}\left\{ \abs{\mathcal{L}_{k,\tau}} \right\} & \label{eq:templength}\\
\Delta_{\bm{k}^*} \sim \mathcal{N} \left(\mu_{\bm{k}^*},\sigma_{\bm{k}^*}^2\right) & \label{eq:tempqualitystart}\\
\mu_{\bm{k}^*} = mean\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\sigma_{\bm{k}^*} = std\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\bm{mr}_{\bm{k}^*} = \bigcup_{k\in\bm{k}^*}mr_k  &\\
\bm{q}_{\bm{k}^*}  =\bigcup_{\alpha\in\mathcal{A}_{ij}}q_{\alpha,ij} & \label{eq:tempqualityend}\\
% \Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
% \mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
% \sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
% l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \\
l^* = \arg\left( \max_{\forall l}\left(\Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)  \right) & \label{eq:optl}\\
Rank_{l^*} = R\left( F\left( ms_{l^*} \right) \right) & \\
\mathcal{L}_{l^*} = \abs{\mathcal{L}_{l^*,\tau}} & \\
m \in \left\{ l^*,\bm{k}^* \right\} \label{eq:newdicisionvariable}
\end{numcases}

@@

% \subsubsection{Provider assign task to selected machine} % (fold)
\resume{asparaenum}
\item Assign behavior
\end{asparaenum}
If $mr_k$ is selected by provider of $sc_l$ at time $\tau$, the assign condition is more restrict, it should be changed into $\abs{\mathcal{L}_{k,\tau}} = \abs{\mathcal{G}_{k,\tau}} = \abs{\mathcal{H}_{k,\tau}} = 0$, for the capacity dominance feature of service-call, we need to assign this type of job one by one. Then, the provider of $mr_k$ should change the predecessor set:
\begin{equation}
	\mathcal{P}_l := \mathcal{P}_l\cup \mathcal{L}_{k,\tau} \cup \mathcal{H}_{k,\tau}
\end{equation}
and all the task assign after $\tau$, we say $\tau'>\tau$ will set:
\begin{equation}
	\mathcal{P}_{ij} := \mathcal{P}_{ij}\cup \left\{ sc| sc\in\mathcal{L}_{k,\tau'},sc \text{ is service-call} \right\} \cup \mathcal{H}_{k,\tau'}
\end{equation}
And $A_{k,\tau}$ will be changed with the same amount in \autoref{eq:capq}--\ref{eq:cap0}.

Assign $t_{ij}$ to $ms_l$

Assign $t_{ij}$ to $ms_l$ is very simple and there will be no semi-active status for $t_{ij}$, hence it will add to $\mathcal{G}_{k,\tau}$ if $\abs{\mathcal{G}_{k,\tau}}=0$, or to $\mathcal{L}_{k,\tau}$ otherwise.
% \begin{subnumcases}{}
% \mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{sc_{l}\} & if $\abs{\mathcal{G}_{k,\tau}}=0$ \\
% \mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{sc_{l}\} & otherwise
% \end{subnumcases}
